Air cargo load and route planning in pickup and delivery operations

### 2023-06-08 CAIE/cie.tex
cie file updated

		\multirow{6}{*}{\it Gurobi* }& \multirow{2}{*}{1200} & $f$ & 14.67   & x       &  20.64  &  x      & 27.97   & x \\ % 
		&        &  {\bf run time (s)}                             & 217     & x       &  304    &  x      & 579     & x \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.59   &         &  20.60  &  x      & 29.10   & x \\ % 
		&        &  {\bf run time (s)}                             & 313     &         &  327    &  x      & 543     & x \\ % 
		\cmidrule(lr){2-9}                              		
		& \multirow{2}{*}{3600}& $f$                               & 14.61   & x       &  20.59  &         & 29.11   & x \\ % 
		&        &  {\bf run time (s)}                             & 297     & x       &  470    &         & 689     & x \\ % 		
		\midrule
		\multirow{6}{*}{\it Shims}   & \multirow{2}{*}{1200} & $f$ & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ % 
		&        & {\bf run time (s)}                              & 18      & 109     &  26     & 160     & 37      & 203   \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ % 
		&        &  {\bf run time (s)}                             & 18      & 107     &  25     & 159     & 37      & 192   \\ % 	
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{3600} & $f$                              & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ %  
		&        &  {\bf run time (s)}                             & 17      & 106     &  26     & 157     & 37      & 181   \\ %  
		\bottomrule

		&                                       & {\bf Normalized} & 0.99    & x       & 0.99    & x       & 1.00    & x\\
		&                                       & {\bf Speed-up}   & 15.6    & x       & 14.3    & x       & 16.3    & x\\

@@

\subsubsection{Proposed K! strategy assessment}

@@

	For this achievement, we ran {\it Shims} in 5 scenarios with 7 instances each, and 3 volume surpluses, collecting the averages of the best tour result and the least cost tour result.

@@

			\multirow{2}{*}{$1.2$}   & Least cost    & 8.54    & 11.63   & 12.97   & 13.43  & 12.36 & 58.93 &       \\ 
			& Best in $K!$  & 8.54    & 12.26   & 13.23   & 14.53  & 13.42 & 61.98 & 5.2\%  \\ 
			\midrule[.1pt]	
			\multirow{2}{*}{$1.5$}   & Least cost    & 10.89   & 11.83   & 16.74   & 18.01  & 18.89 & 76.36 & \\ 	
			& Best in $K!$  & 11.33   & 11.83   & 17.00   & 18.21  & 20.45 & 78.82 &  3.2\%  \\ 
			\midrule[.1pt]	
			\multirow{2}{*}{$2.0$}   & Least cost    & 17.78   & 24.40   & 26.36   & 27.01  & 23.94 & 119.49 &  \\ 
			& Best in $K!$  & 17.78   & 25.25   & 26.38   & 28.98  & 26.08 & 124.47 & 4.2\%   \\ 		                         
			\midrule[.1pt]
			\multicolumn{8}{r}{{\bf K! strategy advantage}}                                              & {\bf 4.2}\% \\

@@

	It is important to report that the best tour found in each test was seldom the tour with the lowest cost (the minimal cost tour without considering the CG deviation), but any of the first 25\% of the best tours. This indicates that our strategy of enumerating and solving all tours was assertive, although it is possible to devise a more proactive strategy to discard most of the higher-cost tours and improve performance. This must be one of the next steps in this research.

	If a posterior application of this method requires 8, 9, or more nodes, it is possible to use this 25\% as a threshold to discard the higher-cost tours and keep the run time within an operational acceptable limit for the client.

@@

@@

	All {\it Shims} executions consumed at most 1.5 GiB, requiring 5 GiB of total memory.
	These details are important for a future application to adequately dimension the computer to be used.

>>>>

		\multirow{6}{*}{\it Gurobi* }& \multirow{2}{*}{1200} & $f$ & 14.67   & x       &  20.64  &  x      & 27.97   & x \\ % 
		&        &  {\bf run time (s)}                             & 217     & x       &  304    &  x      & 579     & x \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.59   &         &  20.60  &  x      & 29.10   & x \\ % 
		&        &  {\bf run time (s)}                             & 313     &         &  327    &  x      & 543     & x \\ % 
		\cmidrule(lr){2-9}                              		
		& \multirow{2}{*}{3600}& $f$                               & 14.61   & x       &  20.59  & 18.36   & 29.11   & x \\ % 
		&        &  {\bf run time (s)}                             & 297     & x       &  470    & 2241    & 689     & x \\ % 		
		\midrule
		\multirow{6}{*}{\it Shims}   & \multirow{2}{*}{1200} & $f$ & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ % 
		&        & {\bf run time (s)}                              & 18      & 109     &  26     & 160     & 37      & 203   \\ % 
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{2400}& $f$                               & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ % 
		&        &  {\bf run time (s)}                             & 18      & 107     &  25     & 159     & 37      & 192   \\ % 	
		\cmidrule(lr){2-9}                              
		& \multirow{2}{*}{3600} & $f$                              & 14.53   & 13.42   &  20.45  & 18.00   & 28.98   & 26.08 \\ %  
		&        &  {\bf run time (s)}                             & 17      & 106     &  26     & 157     & 37      & 181   \\ %  
		\bottomrule

		&                                       & {\bf Normalized} & 0.99    & x       & 0.99    & 0.98    & 1.00    & x\\
		&                                       & {\bf Speed-up}   & 15.6    & x       & 14.3    & 14.3    & 16.3    & x\\

@@

\subsubsection{Proposed $S_K$ strategy assessment}

@@

	For this achievement, we collected {\it Shims} results from tables \ref{tab:20}, \ref{tab:50}, and \ref{tab:100}, gathering the best tour results and the least cost results to assemble Table \ref{tab:20least}.

@@

			\multirow{2}{*}{$1.2$}   & Least cost    & 8.54    & 11.63   & 12.97   & 13.43  & 12.36 & 58.93 &       \\ 
			& Best in $S_K$  & 8.54    & 12.26   & 13.23   & 14.53  & 13.42 & 61.98 & 5.2\%  \\ 
			\midrule[.1pt]	
			\multirow{2}{*}{$1.5$}   & Least cost    & 10.89   & 11.83   & 16.74   & 18.01  & 18.89 & 76.36 & \\ 	
			& Best in $S_K$  & 11.33   & 11.83   & 17.00   & 18.21  & 20.45 & 78.82 &  3.2\%  \\ 
			\midrule[.1pt]	
			\multirow{2}{*}{$2.0$}   & Least cost    & 17.78   & 24.40   & 26.36   & 27.01  & 23.94 & 119.49 &  \\ 
			& Best in $S_K$  & 17.78   & 25.25   & 26.38   & 28.98  & 26.08 & 124.47 & 4.2\%   \\ 		                         
			\midrule[.1pt]
			\multicolumn{8}{r}{\boldm{$S_K$} {\bf strategy advantage}}                                              & {\bf 4.2}\% \\

@@

@@

It is important to report that the best tour found in each test was seldom the tour with the lowest cost (the minimal cost tour without considering the CG deviation), but any of the best tours. This indicates that our strategy of enumerating and solving all tours was assertive, although it is possible to devise a more proactive strategy to discard most of the higher-cost tours and improve performance. This must be one of the next steps in this research. If effective, this strategy may permit posterior applications for eight or more nodes.

@@

All {\it Shims} executions consumed at most 1.5 GiB, requiring 5 GiB of a computer total memory.
These details are important for a future application to adequately dimension the machine to be used.
